\documentclass[12pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage{float}
\usepackage{amsmath,latexsym,amssymb}
\usepackage{epsfig}
\usepackage{hyperref}
\usepackage{color}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\textwidth}{7.1in}
\setlength{\topmargin}{-1in}
\setlength{\textheight}{9in}
\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}
\newcommand{\red}[1]{{\color{red} #1}}
\newcommand{\blue}[1]{{\color{blue} #1}}




\begin{document}
%From: J¸rgen Symanzik <juergen.symanzik@usu.edu>
%Subject: COST: Your manuscript entitled Visual Statistical Inference for High Dimension, Small Sample Size Data
%Date: September 29, 2013 1:31:58 PM CDT
%To: "Niladri Roy Chowdhury" <niladri.ia@gmail.com>
%
%CC: juergen.symanzik@usu.edu
{\large\bf Author's Response to Review}
\bigskip

We appreciate the helpful reviews. The paper has been revised following these suggestions as closely as possible. Specific changes made in response to each reviewer comment are shown in {\color{blue} blue} below.

\bigskip
\textbf{Response to Co-editor:}\\

I have one question regarding the colors: How well can those be distinguished when printed in grayscale? If many of the figures lose their meaning when printed in grayscale, you should consider to have this article published in color for the print edition. The online edition will be published in color in any case. \\

{\color{blue} We plan to print the figures in color which will loose meaning if printed in grayscale. } \\

Some comments regarding the citations/references: \\

{\color{blue} All the citations described below has been modified:} \\

- For books (such as Ripley \& Wickham) list the city of publication. \\

- For R packages (such as fpc, ggplot2, tourr), also list the url for the package. See how R itself recommends to cite the packages via the citation("package") expression. \\

- In case there exists a supporting publication (such as for ggplot2 \& tourr), cite both, the R package and the publication. \\

- For the JSS article, include the issue number and the url (http://www.jstatsoft.org/v40/i02) to make it easier for readers to access such an article. \\

- Lee \& Cook (2009) needs this information: 
Statistics and Computing
2010, Volume 20, Issue 3, pp 381-392 
omit the URL \\

- Include a URL where readers can obtain your Roy Chowdhury N, Cook D, Hofmann H, Majumder M (2012) technical report. Has this been published elsewhere by now? If so, update the reference. \\ 

- Finally, is 2009 for the R reference still appropriate? Update to something more recent :-) \\

\textbf{Response to Reviewer \#3} \\

Grammatical and typographical errors \\

\begin{itemize}\item Page 2, starting paragraph 2, sentence “There exists no conventional inferential methods which enables us to conclude . . . ” \\– replace “methods” by “method” and “which” by “that” \\

{\color{blue} This is changed in the paper.} \\
\item Page 2, last starting paragraph, the second sentence should read “Visual statistical inference was . . . ” (2009, and formalized and validated by . . . ” \\

{\color{blue} This is changed in the paper.} \\
\item Page 3 second paragraph, third last sentence (and possibly elsewhere) “on wasp data” re- quires the definite article, as in “on the wasp data” to indicate that it is this particular data set that is being referred to. \\

{\color{blue} This is changed in the paper.} \\
\item Page 4, Table 1 caption, the third sentence should read “In conventional testing . . . ” \\

{\color{blue} This is changed in the paper.} \\
\item Page 6, first paragraph of Section 4, should read “in exchange for their efforts” \\

{\color{blue} This is changed in the paper.} \\

\end{itemize}

\end{document}